---
title: "SDS315 HW 3"
author: "Samuel Li"
date: "2/12"
output: pdf_document
---

[https://github.com/SamuelLi1225/SDS-HW3](https://github.com/SamuelLi1225/SDS-HW3)

```{r setup, include=FALSE}
library(ggplot2)
library(mosaic)
library(dplyr)
knitr::opts_chunk$set(fig.height=8, fig.width=12, warning=FALSE, message=FALSE)
```



# Problem 1

## Part A
```{r echo=FALSE}
gas_data <- read.csv("gasprices.csv")
boot_gas <- do(10000) * diffmean(Price ~ Competitors, data = resample(gas_data))
confint(boot_gas, level = 0.95)
```
- **Question:** Do gas stations charge more without competition?
- **Approach:** Used bootstrapped mean difference in gas prices.
- **Results:** Mean difference **-0.0235**, CI **(-0.0555, 0.0080)**.
- **Conclusion:** No strong evidence supporting the claim since CI includes **0**.

## Part B
```{r echo=FALSE}
boot_income <- do(10000) * cor(Price ~ Income, data = resample(gas_data))
confint(boot_income, level = 0.95)
```
- **Question:** Do higher-income areas have higher gas prices?
- **Approach:** Used bootstrapped correlation between price and income.
- **Results:** Correlation **0.396**, CI **(0.200, 0.564)**.
- **Conclusion:** Significant moderate positive correlation, supporting the claim.

## Part C
```{r echo=FALSE}
boot_stoplight <- do(10000) * diffmean(Price ~ Stoplight, data = resample(gas_data))
confint(boot_stoplight, level = 0.95)
```
- **Question:** Do gas stations at stoplights charge more?
- **Approach:** Used bootstrapped mean difference in gas prices at stoplights.
- **Results:** Mean difference **-0.0033**, CI **(-0.0376, 0.0311)**.
- **Conclusion:** No strong evidence supporting the claim since CI includes **0**.

## Part D
```{r echo=FALSE}
boot_highway_access <- do(10000) * diffmean(Price ~ Highway, data = resample(gas_data))
confint(boot_highway_access, level = 0.95)
```
- **Question:** Do gas stations near highways charge more?
- **Approach:** Used bootstrapped mean difference in gas prices near highways.
- **Results:** Mean difference **0.0457**, CI **(0.0089, 0.0817)**.
- **Conclusion:** Significant evidence supporting the claim since CI **excludes 0**.

## Part E
```{r echo=FALSE}
gas_data$BrandGroup <- ifelse(gas_data$Brand == "Shell", "Shell", "Other")
boot_brand <- do(10000) * diffmean(Price ~ BrandGroup, data = resample(gas_data))
confint(boot_brand, level = 0.95)
```
- **Question:** Does Shell charge more than other brands?
- **Approach:** Used bootstrapped mean difference in gas prices between Shell and others.
- **Results:** CI includes **0**, meaning no strong evidence.
- **Conclusion:** The claim is not statistically supported since the CI contains **0**.

# Problem 2

## Part A
```{r echo=FALSE}
sclass_data <- read.csv("sclass.csv")
sclass_filtered <- sclass_data[sclass_data$year == 2011 & sclass_data$trim == "63 AMG", ]
boot_mileage <- do(10000) * mean(~mileage, data = resample(sclass_filtered))
confint(boot_mileage, level = 0.95)
```

## Part B
```{r echo=FALSE}
filtered_mercedes <- read.csv("sclass.csv")
filtered_mercedes <- filtered_mercedes[filtered_mercedes$year == 2014 & filtered_mercedes$trim == "550", ]
filtered_mercedes$isBlack <- filtered_mercedes$color == "Black"
boot_black <- do(10000) * prop(~isBlack, data = resample(filtered_mercedes))
confint(boot_black, level = 0.95)
```

# Problem 3

## Part A
```{r echo=FALSE}
nbc_data <- read.csv("nbc_pilotsurvey.csv")
nbc_filtered <- nbc_data[nbc_data$Show %in% c("My Name is Earl", "Living with Ed"), ]
boot_happy <- do(10000) * diffmean(Q1_Happy ~ Show, data = resample(nbc_filtered))
confint(boot_happy, level = 0.95)
```
- **Question:** Which show makes people happier?
- **Approach:** Used bootstrapped mean difference in happy responses.
- **Results:** Mean difference **-0.149**, CI **(-0.3992, 0.0988)**.
- **Conclusion:** No statistical evidence supporting a happiness difference since CI contains **0**.

## Part B
```{r echo=FALSE}
boot_annoyed <- do(10000) * diffmean(Q1_Annoyed ~ Show, data = resample(nbc_filtered))
confint(boot_annoyed, level = 0.95)
```
- **Question:** Which show is more annoying?
- **Approach:** Used bootstrapped mean difference in annoyed responses.
- **Results:** Mean difference **-0.271**, CI **(-0.5174, -0.0229)**.
- **Conclusion:** Significant evidence that "The Apprentice: Los Angeles" is more annoying.

## Part C
```{r echo=FALSE}
nbc_filtered <- nbc_data[nbc_data$Show == "Dancing with the Stars", ]
nbc_filtered$ConfusingBinary <- nbc_filtered$Q2_Confusing > 3
boot_confusing <- do(10000) * prop(~ConfusingBinary, data = resample(nbc_filtered))
confint(boot_confusing, level = 0.95)
```
- **Question:** How many viewers found "Dancing with the Stars" confusing?
- **Approach:** Used bootstrapped proportion of confused responses.
- **Results:** Proportion **0.0773**, CI **(0.0387, 0.1160)**.
- **Conclusion:** A small proportion of viewers found the show confusing since CI is all above **0**.

# Problem 4:
```{r echo=FALSE}
ebay_data <- read.csv("ebay.csv")
ebay_data$revenue_ratio <- ebay_data$rev_after / ebay_data$rev_before
boot_ebay <- do(10000) * diffmean(revenue_ratio ~ adwords_pause, data = resample(ebay_data))
confint(boot_ebay, level = 0.95)
```
- **Question:** Does paid search improve revenue?
- **Approach:** Used bootstrapped mean difference in revenue ratios before and after ad pause.
- **Results:** Mean difference **-0.05228**, CI **(-0.0914, -0.01421)**.
- **Conclusion:** The negative effect suggests pausing ads lowers revenue since CI does not contain **0**.
